---
title: "PS2"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)
```



```{r DL data and regress, echo=TRUE}
execomp <- read.csv("C:\\Users\\Eli\\Dropbox\\ERG\\Spring19\\PublicEcon\\HW2\\execucomp.csv")
sum(execomp$TOTAL_SEC==0, na.rm = 1)


```

1. CEO Pay response to the 2013 US tax increase
The goal of this exercise is to repeat the Goolsbee (2000) analysis of CEO pay around the
2013 top tax rate increase (instead of the 1993 top tax rate increase as Goolsbee did).
a) First stage: Using online sources, calculate the change in the top marginal tax rate for
labor income compensation generated by the 2013 tax increase including both the change in the
Federal tax rate, and the Aﬀordable Care Act surtax. How does the size of the change compare
with the 1993 tax increase from Goolsbee (2000) study?



```{r plot and Q1a, echo=FALSE}
ggplot(execomp, aes(EXEC_FULLNAME,TOTAL_SEC)) + geom_point(aes (colour = YEAR))# )  + facet_grid(YEAR ~ .)

Q1a <- data.frame(c(1992, 1993, 2012, 2013),c(.31, .396, .35, .396+.038))

kable(Q1a)
```
b) Timing of the reform: search online to ﬁgure out whether people knew in advance that
the 2013 tax increase would take place? Is it reasonable to think that executives could respond
to the tax change as they did with the 1993 tax change?
```{Q1b}


```
```{Q1c}
```
```{Q1d}
```
Q1d <- data.frame(c("",1991, 1992, 1993, 1994, 1995, 2010,2011,2012,2013,2014),c("Taxable Income", 911, 1153, 974, 965, 1173, ))
print("https://en.wikipedia.org/wiki/Income_tax_in_the_United_States#Marginal_tax_rates_since_2008")
kable 
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
adding a line
