---
title: "PS2"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('dplyr')
library(ggplot2)
library(knitr)
#library(TeX)
```



```{r DL data and regress, echo=TRUE}
execomp <- read.csv("C:\\Users\\Eli\\Dropbox\\ERG\\Spring19\\PublicEcon\\HW2\\execucomp.csv")
sum(execomp$TOTAL_SEC==0, na.rm = 1)


```

1. CEO Pay response to the 2013 US tax increase
The goal of this exercise is to repeat the Goolsbee (2000) analysis of CEO pay around the
2013 top tax rate increase (instead of the 1993 top tax rate increase as Goolsbee did).
a) First stage: Using online sources, calculate the change in the top marginal tax rate for
labor income compensation generated by the 2013 tax increase including both the change in the
Federal tax rate, and the Affordable Care Act surtax. How does the size of the change compare
with the 1993 tax increase from Goolsbee (2000) study?



```{r plot and Q1a, echo=FALSE}
#  ggplot(execomp, aes(EXEC_FULLNAME,TOTAL_SEC)) + geom_point(aes (colour = YEAR))# )  + facet_grid(YEAR ~ .)


```
b) Timing of the reform: search online to figure out whether people knew in advance that
the 2013 tax increase would take place? Is it reasonable to think that executives could respond
to the tax change as they did with the 1993 tax change?

```{r Q1c}
```

```{r Q1d, echo=FALSE}
execomp %>% group_by(YEAR) %>% summarise('Taxable Income'=mean(na.omit(TOTAL_SEC)),SALARY=mean(na.omit(SALARY)),Bonus=mean(na.omit(BONUS)), LTIP=mean(na.omit(LTIP)),Options=mean(na.omit(OPTION_AWARDS_FV)),'Other Compensation'=mean(na.omit(OTHCOMP))) %>% t()

print("https://en.wikipedia.org/wiki/Income_tax_in_the_United_States#Marginal_tax_rates_since_2008")

Q1d <- data.frame(c("",1991, 1992, 1993, 1994, 1995, 2010,2011,2012,2013,2014),c("Taxable Income", 911, 1153, 974, 965, 1173,999,999,999,999,999))

```

asdlfakjsdflkj

Taxable income 911 1,153 974 965 1,173
Salary 347 336 336 351 373
Bonus 198 207 241 284 330
LTIP payout 57 72 57 64 89
Options exercised 268 496 293 235 381
Other income (nontaxed) 36 37 66 54 78


